\begin{enumerate}
\item A. Chandrashekaran, I. Lane, ``\emph{Auto-ML for Automated Optimization of Speech Recognition on Mobile Devices}'', GTC 2018 (Poster)
\item K. Han, A. Chandrashekaran, J. Kim, I. Lane, ``\emph{Densely Connected Networks for Conversational Speech Recognition}'', Interspeech 2018 (Submitted)
\item K. Han, A. Chandrashekaran, J. Kim, I. Lane, ``\emph{The CAPIO 2017 Conversational Speech Recognition System}'', ArXiv Preprint \emph{1801.00059} 
\item A. Chandrashekaran, I. Lane ``\emph{Speeding up Hyper-parameter Optimization by Extrapolation of Learning Curves using Previous Builds}'', ECML 2017
\item A. Chandrashekaran, I. Lane, ``\emph{Hierarchical Constrained Bayesian Optimization for Feature, Acoustic Model and Decoder Parameter Optimization}'', Interspeech 2017.
\item  A. Chandrashekaran, I. Lane, ``\emph{Automated optimization of decoder hyper-parameters for online LVCSR}'', Spoken Language Technologies Workshop (SLT 2016).
\item  A. Chandrashekaran, I. Lane, ``\emph{Automated Feature and Model Optimization for Task-specific Acoustic Models}'', BayLearn 2015 (Poster).

\item D. Cohen, A. Chandrashekaran, I. Lane, A. Raux, ``\emph{The hri-cmu corpus of situated in-car interactions.}'', Proceedings for International Workshop Series on Spoken Dialogue Systems Technology (IWSDS 2014).
 
 \item I. Lane, V. Prasad, G. Sinha, A. Umuhoza, S. Luo, A. Chandrashekaran, A. Raux, ``\emph{HRItk: the human-robot interaction ToolKit rapid development of speech-centric interactive systems in ROS.}'' NAACL-HLT Workshop on Future Directions and Needs in the Spoken Dialog Community: Tools and Data (NAACL-HLT 2012). Association for Computational Linguistics.
 \end{enumerate}

%{\bf To be submitted}{}\\ 
%\vspace{-1.0em}
%\begin{enumerate}
 %\item Y. Wang and {\bf M. Zeng}, ``\emph{Improving Text Classification by Capturing Local Feature from Word Sequences}", SIAM International %Conference on Data Mining (SDM 2016)
 
% \item {\bf M. Zeng}, L. T. Nguyen, O. J. Mengshoel and J. Zhang ``\emph{AttriNet: Learning Mid-Level Features for Human Activity Recognition with Deep Belief Networks}", International Conference on Mobile Systems, Applications, and Services (MobiSys 2016)
% \end{enumerate}








